---
title: "Tiange hw 2"
author: "Tiange Yang"
date: "10/4/2019"
output: html_document
---

```{r setup, include=FALSE}
require(rgdal)
require(leaflet)
require(leaflet.extras)
require(dplyr)
require(readxl)
require(stringr)
```

## By this assignment, I am going to show you the commute situation in HongKong. 
## load data and get summary.hk.delivery is the data of post boxes and facilities. hk.house is public houses where people mainly live in .HK.C are roads and average speed. 
```{r}
hk.delivery <-  data.frame(read.csv("/Users/tiangeyang/Desktop/hw2/Street_Posting_Boxes_in_Hong_Kong.csv"))
str(hk.delivery)
levels(hk.delivery$District)
hk.house<-data.frame(read.csv("/Users/tiangeyang/Desktop/hw2/Public_Housing_Estates_in_Hong_Kong.csv"))
str(hk.house)
hk.c<-readOGR('/Users/tiangeyang/Desktop/hw2/TD_SpeedMap.geojson.json')
plot(hk.c)
```


##blank Map with Basemap
```{r}
leaflet() %>%
  addProviderTiles(providers$OpenStreetMap.HOT)
```
## Map delivery facilities in each district by points
```{r}
pal.d <- colorFactor(topo.colors(18),c("CENTRAL AND WESTERN","EASTERN","ISLANDS DISTRICT","KOWLOON CITY","KWAI TSING", "KWUN TONG","NORTH","SAI KUNG","SHA TIN","SHAM SHUI PO" ,"SOUTHERN", "TAI PO","TSUEN WAN","TUEN MUN","WAN CHAI","WONG TAI SIN","YAU TSIM MONG","YUEN LONG"))
#Map points
leaflet() %>%
  addProviderTiles("OpenStreetMap.DE") %>%
  #add a layer of points
  addCircleMarkers(data = hk.delivery, 
                   lng = ~Longitude, 
                   lat = ~Latitude , 
                   radius = 1,
                   color = ~pal.d(District),
                  clusterOptions = markerClusterOptions()) %>%
  #add legend
  addLegend(position = "topright", 
            pal = pal.d, 
            values = hk.delivery$District, 
            title = "HK District")
```
## Map main commute networks by polylines. 
```{r}
leaflet(data = hk.c) %>%
  addProviderTiles("OpenStreetMap.DE") %>%
  #add a layer of lines
  addPolylines(color = "Brown")
```
## Map public houses catagorized by year and block. Uers can choose basemap and group.
```{r}
pal.h<-colorNumeric(palette = "Blues",domain = hk.house$Year_of_Intake_en)
pal.hb<-colorNumeric(palette = "Reds",domain = hk.house$No__of_Blocks,3,na="white")
#Map
leaflet() %>%
  addProviderTiles("OpenStreetMap.HOT", group = "osm.H") %>%
  addProviderTiles("Esri.NatGeoWorldMap", group = "otm") %>%
  addProviderTiles("Stamen.Toner", group = "s.t") %>%
#add a layer of points
  addCircleMarkers(data = hk.house, 
                   lng = ~Longitude, 
                   lat = ~Latitude, 
                   fillOpacity = .8,
                   radius = 1,
                   color = ~pal.h(Year_of_Intake_en),
                   group='House Year') %>%
#add legend
  addLegend(position = "topleft", 
            pal = pal.h, 
            values = hk.house$Year_of_Intake_en, 
            title = "HK House Year",
            group='House Year') %>%
  
#add a layer of points
  addCircleMarkers(data = hk.house, 
                   lng = ~Longitude, 
                   lat = ~Latitude, 
                   fillOpacity = .4,
                   radius = 1,
                   color = ~pal.h(No__of_Blocks),
                   group='#Block') %>%
#add legend
  addLegend(position = "topleft", 
            pal = pal.hb, 
            values = hk.house$No__of_Blocks, 
            title = "#Block",
            group='#Block') %>%
  
#add layers control
  addLayersControl(
    baseGroups = c("snm.H", "otm", "s.t"),
   overlayGroups = c("HK House Year", "#Block"),
   options = layersControlOptions(collapsed = FALSE)
  )

```